% Felix Jancso-Szabo's Resume
% URL: https://github.com/fJancsoSzabo/Resume
% Forked from James Pearson Hughes's resume
% URL: https://github.com/xiongchiamiov/Resume
\documentclass[margin,line]{resume}

\usepackage{newtxmath}
\usepackage{newtxtext}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage{enumitem}

\begin{document}

\name{\huge \sc{Felix Jancso-Szabo}\vspace{2mm}}
{
    \hfill 3A Computer Engineering \vspace{0mm} \\\vspace{0mm}
    \hfill felix.ajs@gmail.com       \vspace{0mm}\\\vspace{0mm}
    \hfill https://github.com/fJancsoSzabo \vspace{0mm}\\\vspace{-9mm}
}

\begin{resume}

    %__________________________________________________________________________________________________________________
    % Summary
    \section{\mysidestyle \textbf{\large{S}\small{UMMARY}}}

    \begin{tightemizenoindent}
    \item Highly proficient with \textbf{Go}, \textbf{Python}, bare metal \textbf{C}, and \textbf{Assembly}.
    \item Experienced with \textbf{MySQL}, \textbf{Bash}, \LaTeX, and \textbf{PHP}.
    \item Used \textbf{Postman} for API testing and development.
    \item Four month's experience using \textbf{CircleCI} for testing and deployment at Reebee.
    \item Over two years of experience with \textbf{git} through personal, professional and academic use.
    \item \textbf{Subversion} and \textbf{CVS} experience through academic and professional usage, respectively.
    \item Experience using \textbf{Jetbrains IDE's}, \textbf{Keil \pmb{\si\micro}Vision}, \textbf{Eclipse}, as well as text editors and command line tools to develop and debug a variety of languages.
    \item Worked on teams using Agile development, using \textbf{Pivotal} and \textbf{Jira} to track issues.
    \end{tightemizenoindent}

    \vspace{-1mm}

\sectionline

    %__________________________________________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle \textbf{\large{W}\small{ORK}\\ \large{E}\small{XPERIENCE}}}

    % Reebee
    \textbf{\listing Reebee} \vspace{2mm}\\\vspace{1mm}%
    \textsl{Test Automation Developer / Backend Developer} \hfill \textbf{September 2017 -- December 2017}\\
    Designed testing framework and increased CI usage at a digital flyer startup.\\
    \begin{tightemize}
    \item Created a server-based testing framework to perform integration testing of the Reebee API, based off of JSON specifications.
    \item Created a tool to generate ORM model files for PHP and Go.
    \item Implemented new API endpoints to allow automated creation of client profiles.
    \end{tightemize}

    \vspace{1mm}
    % Clear Blue Technologies
    \textbf{\listing Clear Blue Technologies} \vspace{2mm}\\\vspace{1mm}%
    \textsl{Senior Software Developer} \hfill \textbf{January 2017 -- April 2017}\\
    Designed power management firmware for smart off-grid power controllers. \\
    \begin{tightemize}
    \item Designed a highly configurable module to allow a power supply to be used as a backup energy source.
    \item Co-designed a robust dimming module to prevent flickering in aging and poorly made street lamps.
    \item Produced and maintained comprehensive flowcharts to document algorithms.
    \item Collaborated with multiple teams to isolate and fix reported bugs.
    \end{tightemize}

    \vspace{1mm}
    % ON Semi
    \textbf{\listing ON Semiconductor} \vspace{2mm}\\\vspace{1mm}%
    \textsl{Embedded Firmware Developer} \hfill \textbf{May 2016 -- August 2016}\\
    Implemented interfacing and communication algorithms for hearing aids for the medical devision of a Fortune 1000 semiconductor company. \\
    \begin{tightemize}
    \item Co-designed a Bluetooth Low Energy based protocol to allow wireless configuration of the products.
    \item Extended the hearing aid bootloader to allow firmware updates of all on-board chips.
    \item Refactored bootloader scripts to achieve a 200\% speed increase.
    \item Isolated and patched the source of bus errors using oscilloscopes.\\
    \end{tightemize}

\vspace{-1mm}
\sectionline

    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle \textbf{\large{E}\small{DUCATION}}}

    \textbf{\listing University of Waterloo}, Waterloo, Ontario\vspace{1mm}\\
    \textsl{B.A.Sc of Computer Engineering} \hfill \textbf{September 2015 -- April 2020 (projected)}\vspace{-3mm}\\\vspace{-1mm}%

\sectionline

    %__________________________________________________________________________________________________________________
    % Personal Projects
    \section{\mysidestyle \textbf{\large{P}\small{ERSONAL}\\ \large{P}\small{ROJECTS}}}

    \textbf{\listing Waterloo Engineering Society} \vspace{2mm}\\\vspace{1mm}%
    \textsl{Website Director} \hfill \textbf{September 2017 -- Present}\\
    Maintained and improved the Waterloo Engineering Society Website. \\
    \begin{tightemize}
    \item Rebuilt the website from the ground up, including an overhaul of the content.
    \end{tightemize}

    \textbf{\listing Boolean Algebra System} \vspace{2mm}\\\vspace{1mm}%
    \textsl{Developer}\\
    Built a system to:\\
    \begin{tightemize}
    \item Parse boolean expressions and generate their truth tables.
    \item Simplify boolean expressions using the Quine-McCluskey algorithm.
    \end{tightemize}

\sectionline

    %__________________________________________________________________________________________________________________
    % Interests / Hobbies
    \section{\mysidestyle \textbf{\large{I}\small{NTERESTS  / \\ \large{H}\small{OBBIES}}}}

    \textsl{Euchre, Swimming, Cycling, Engineering Student Lounge \& Student Store Manager.}\\

\end{resume}
\end{document}
